%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,letterpaper,sans,dvipsnames]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

\usepackage{fancyhdr}
\usepackage{xcolor}
\chead{\color{RoyalBlue}G. S. Antell}
% \cfoot{Page \thepage\ of \pageref{LastPage}}

% moderncv themes
\moderncvstyle{fancy}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{blue}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name

% \nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.78,top=1in,bottom=1in]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\hyphenpenalty=10000

% personal data
\name{Gwen S.}{Antell}
% \title{Resumé title}             
%\address{St John's College \\ St Giles}{OX1 3JP, Oxford}{United Kingdom}% "postcode city" and "country" arguments can be omitted or provided empty
\email{gwen.antell\\@earth.ox.ac.uk}                           
% \phone[mobile]{}      % the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\homepage{gwenantell.com}                    
%\social[linkedin]{john.doe}                 
% \social[twitter]{GwenAntell}        
%\social[github]{GwenAntell}        
% \extrainfo{additional information}    
% \photo[64pt][0.4pt]{Antell_profile_small}              % '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
% \quote{Some quote}     

\usepackage[backend=bibtex, isbn=false, bibstyle=numeric, sorting=none, defernumbers=true, maxbibnames=5]{biblatex} 
\bibliography{presentations_publications.bib}

  
% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

\thispagestyle{empty}

\makecvtitle

\section{Education}
\cventry{2017--Present}{DPhil}{University of Oxford}{UK}{}{Departments of Earth Sciences and Zoology}  % arguments 3 to 6 can be left empty
\cventry{2012--2016}{B.S.}{Yale University}{USA}{\textit{magna cum laude}}{Ecology \& Evolutionary Biology (with distinction) and Geology \& Geophysics}

\section{PhD thesis}
\cvitem{Title}{\emph{Macroecological consequences of biotic and abiotic factors in marine communities through time}}
\cvitem{Supervisors}{Erin Saupe (Earth Sciences) \& Tim Coulson (Zoology)}
\cvitem{Research interests}{ % 
\begin{itemize}
\item Invertebrate paleontology and paleoecology
\item Inferential statistics on time series and multivariate data
\item Biodiversity across spatial, temporal, and taxonomic scales
\end{itemize}
}

\section{Employment}
\cventry{2017--Present}{Graduate teaching assistant}{Earth Sciences}{Oxford}{}{
Labs, tutorials, and field courses about evolution and past environments.}

\cventry{2016--2017}{Geoscientists-in-the-Parks Intern}{US National Park Service, Geologic Resources Division}{Florissant National Monument}{CO}{Research, exhibit design, and geoheritage resource surveys.}

\cventry{2013--2016}{Collections Assistant}{Yale Peabody Museum of Natural History, Invertebrate Paleontology Division}{New Haven}{CT}{Described new fossil species, cataloged specimens, and hosted public tours.}

% \cventry{2015--2016}{Freshmen Counselor}{Yale College}{New Haven, CT}{}{Academic and personal % advising to freshmen; welfare role under the Dean's office.}
% {Description line 1\newline{}Description line 2}

\section{Leadership}
\cvitem{Divisional Equality, Diversity, \& Inclusion Fellow}{serving the STEM division EDI Steering Group and contributing to Oxford's 3-year strategic plan, 2020--2021.}
\cvitem{Co-chair}{Working group on racial diversity and inclusion in Earth Sciences Dept., Oxford, 2019--2020. Co-authored report of 42 action item recommendations.}
\cvitem{Representative for graduate students}{Equality Committee, Earth Sciences Dept., Oxford, 2017--Present. Changed policies and liaised with students.}
\cvitem{Representative for Earth Sciences}{Divisional Joint Consultative Committee, representing graduate student interests, 2018--2020.}
\cvitem{President}{St John's College, Middle Common Room Committee (graduate student body), 2018--2019; \textbf{Disabled students' officer} 2017--2018.}
\cvitem{Women's Leadership Forum facilitator}{St John's College grad.\ students, 2018.}
\cvitem{President}{Yale Ecology and Evo.\ Bio.\ Group, 2015--2016; member 2013--2016.}
\cvitem{Secretary}{Connecticut Entomological Society, 2015--2016; member 2013--2016}

\pagebreak

% bibliography
\nocite{*}
\printbibliography[type=article, title={Publications}] % , resetnumbers=true
\printbibliography[type=inproceedings, title={Conference talks}, resetnumbers=true] 

\section{Awards}
\subsection{Scholarships}
\cvitemwithcomment{}{Clarendon Fund Scholarship}{2017--Present}
\cvitemwithcomment{}{St John's College Alumni Scholarship}{2017--Present}
\cvitemwithcomment{}{NSF Graduate Research Fellowship Program (declined)}{2017}
\cvitemwithcomment{}{Jerry (1953) and Jackie Inskeep Scholarship Fund}{2013-2016}
\cvitemwithcomment{}{Summer Environmental Fellowship, Yale}{2014}
\cvitemwithcomment{}{US National Merit Scholarship}{2012}
\subsection{Grants}
\cvitemwithcomment{}{Burdett-Coutts Grant, Earth Sciences, of Oxford (\pounds 1,650)}{2019}
\cvitemwithcomment{}{Postgraduate Special Grant, St John's College (\pounds 1,250)}{2018}
\cvitemwithcomment{}{Travel Grant, Palaeontological Association (\pounds 300)}{2018}
\cvitem{}{Ernst Mayr travel grant for animal systematics, Museum of Comparative Zoology, Harvard University (\$1,100) \hspace{18 pc} {\small \textit{2016}}}
% \cvitemwithcomment{}{Pierson College Richter Fellowship (\$500)}{2015}
\cvitemwithcomment{}{Yale Science Center Int'l Fellowship (\$3,870; \$4,300)}{2014, 2015}
\cvitemwithcomment{}{Yale Freshmen Summer STEM Research Fellowship (\$4,300)}{2013}
\subsection{Awards}
\cvitem{}{Winifred Goldring Award for outstanding female paleontology student; conferred by Association for Women Geoscientists and Paleontological Society \hspace{3 pc} {\small \textit{2021}}}
\cvitemwithcomment{}{1st place student talk in Geobiology \& Geomicrobiology, GSA meeting}{2020}
\cvitemwithcomment{}{Oxford Earth Sciences award for equality, diversity, \& inclusion}{2020}
\cvitemwithcomment{}{1st place student talk, North American Paleontological Convention}{2019}
\cvitem{}{D.\ E.\ Chantler Award for ``the Yale Senior who has best exemplified qualities of courage, strength of character, and high moral purpose'' \hspace{7 pc} {\small \textit{2016}}} % Yale 
\cvitemwithcomment{}{W. R. Belknap Prize for excellence in a biology thesis, Yale}{2016}
\cvitemwithcomment{}{1st place student speed talk, Connecticut Entomological Society}{2015}
% commended talk, CPEG

\section{Invited talks}
\cvitem{Research seminar}{Sheffield University ecology \& conservation series, Oct 2021.}
\cvitem{Research seminar}{Yale Earth and Planetary Sciences seminar series, May 2021.}
\cvitem{Research seminar}{Harvard paleobiology joint lab groups (Museum of Comparative Zoology and Dept.\ Organismic \& Evolutionary Biology), Nov 2020.}
\cvitem{EDI talk}{``Decolonizing ecology and conservation science,'' Zoological Society of London (Feb 2021) and Oxford Zoology Dept.\ (July 2020).}
% \cvitem{Seminar invitation}{U. of Manchester; \textbf{panel discussion} at U. of Oxford, Earth Sciences. Talk on diversity and inclusion in geosciences, 2020.}
\cvitem{Public lecture}{``Science Short'' research talk on climate change and ocean life, Oxford University Museum of Natural History, 4 Jan 2020.}
\cvitem{Student speaker}{Oxford Geology Group annual symposium, 2019.}
\cvitem{Alumni speaker}{Yale Peabody Museum 150th Anniversary Symposium. One of two recent student graduate speakers, Verrill Medal symposium, 2016.}
% A coexistence story: East African Hornbill niche partitioning. Pierson College Mellon Forum, 2016

\section{Software}
\cvitem{}{Developer of \textit{kerneval} R package for kernel density estimation \href{https://github.com/GwenAntell/kerneval}{[link]}}

\section{Other writing}
% \printbibliography[type=misc, title={Other writing}, resetnumbers=true]
\cvitem{}{(Not peer-reviewed.)}
\cvitem{}{S Greene, \textbf{G Antell}, \textit{et al.} ``Safety and belonging in the field: a checklist for educators.'' \textit{EarthArXiv (2021).} \href{https://doi.org/10.31223/X53P6H}{DOI: 10.31223/X53P6H}.}
\cvitem{}{\textbf{G Antell}. ``All colours of pride.'' Rainbow Research blog series, journal of \textit{Methods in Ecology \& Evolution} (2021). \href{https://methodsblog.com/2021/06/28/rainbow-research-all-colours-of-pride/}{URL: https://methodsblog.com/2021/06/28}.}
\cvitem{}{B Fernando and \textbf{G Antell}. ``Recommendations for improving racial equality, diversity, and inclusion in the Department of Earth Sciences, University of Oxford.'' Public report (2021). Available at: \href{https://www.earth.ox.ac.uk/2020/06/department-of-earth-sciences-releases-report-of-ad-hoc-working-group-on-bame-issues/}{\textit{https://www.earth.ox.ac.uk/2020/06}}.}

\section{Professional training}
\cvitem{Teaching certification}{SEDA Supporting Learning award in higher education (Descriptor 1 of  UK Professional Standards Framework), 2020.}
\cvitem{Science communication and science policy}{``Reclaiming STEM'' 4-part workshop series, run by and for minorities in STEM. Held remotely, 2020.}
\cvitem{Wilderness First Responder}{80-hour emergency medicine certification with wilderness upgrade, maintained valid 2017--Present.}
\cvitem{Science communication for children, STEM Ambassador training, University teaching}{Individual workshops, University of Oxford, Jan--Feb 2019.}
% \cvitem{Science communication for children}{University of Oxford Museum of Natural History, workshop attended 25 Feb 2019.}
% \cvitem{STEM Ambassador training}{University of Oxford, workshop 23 Jan 2019.}
% \cvitem{University teaching}{University of Oxford, workshop attended 20 Feb 2019.}
%\cvitem{Oxford ApplyED (Equality and Diversity) conference}{November 2017.}
% \cvitem{Oxford Disability Law and Policy Conference}{February 2018.}
% \cvitem{RevBayes Bayesian phylogenetic inference}{U.\ Bristol, 1--3 May 2018}
% \cvitem{Mixed-effects models and smart modelling techniques in R}{University of Oxford, 17--20 Apr 2018}

\section{Service}
\cvitem{Palaeontological Association}{Peer review for \textit{Palaeontology}. Session chair for annual meeting, 2020.}
\cvitem{Student representative}{Departmental committees for Equality, Graduate Students, and Teaching; divisional committee for Graduates; 2017--Present. Graduate President on all St John's College committees, 2017--2018.}

\section{Outreach \& advocacy}
% \cvitem{International Assoc.\ of Geoscience Diversity}{member 2018--Present.}
\cvitem{Biology LGBTQ+ Network}{Co-organiser for 2020 LGBT STEM Day symposium at Oxford (cancelled due to COVID-19). £1,000 in grant funding acquired.}
% \cvitem{Report author \& panelist}{Recommendations on racial \& ethnic EDI in Earth Sciences Dept., Oxford, 2020. Available at \href{https://www.earth.ox.ac.uk/2020/06/department-of-earth-sciences-releases-report-of-ad-hoc-working-group-on-bame-issues/}{\textit{https://www.earth.ox.ac.uk/2020/06}}.}
\cvitem{Activity leader}{Super Science Saturday, Oxford University Museum of Natural History, 9 March 2019. Ran activity booth with estimated 3,600 attendees.}
\cvitem{Instructor}{UNIQ summer school, Oxford broadening access program; 2018, 2019. Designed classroom activities and assistant taught a local geology fieldtrip.}
\cvitem{Edinburgh Marathon}{\pounds 750 raised for the Juvenile Diabetes Research Foundation, as an athlete with juvenile (type 1) diabetes. Sub 4-hour finishing time. May 2019.}
\cvitem{March For Science}{Activity leader for the CU Boulder Museum of Natural History, Denver 2017. Support of the American Geophysical Union, London 2018.}
\cvitem{Tough Mudder}{\$1,200 raised for American Diabetes Assoc. Sacramento 2017.}

\section{Field work}
\cvitem{Graduate instructor}{Earth Sciences undergraduate field course. Isle of Arran, UK. 1 week, 2019 (2020 cancelled due to COVID-19). Mapping and interpretation.}
\cvitem{Graduate instructor}{Earth Sciences undergraduate course. Dorset, UK. 1 week, 2018, 2019, 2020 (virtual). Introduction to field skills and sedimentology.}
\cvitem{Stratigraphic paleobiology}{Paleontological Society graduate field course. Bitterroot Mountains, MT. 2 weeks, 2017. Sequence strat.\ and logging sections.}
% \cvitem{Global tectonics}{Yale course. Sicily, Italy. 2 weeks, 2016.}
\cvitem{Wildlife research}{Independent research on bird behavior, Jetz Lab. Kenya: Lale'enok Resource Centre, 2 mo., 2015; Mpala Research Centre, 3 mo., 2014.}	
% \cvitem{Sedimentary geology}{Yale course. Barbados. 2 weeks, 2015.}

\end{document}


%% end of file `template.tex'.